### 2023-02-13 article.tex
Fix curly braces

When the author of code can be contacted,
there will be users asking for technical support 
(against which a 'no' is just fine (\cite{barnes2010publish}))
One solution for the author is to ignore such emails (as is done in a third
of all cases (\cite{teunis2015corresponding})):
it can be argued that no energy should be wasted on published code
and work on something new instead.
However, see \cite{barnes2010publish for a better way to deal with this problem.

>>>>

When the author of code can be contacted,
there will be users asking for technical support.
One solution for the author is to ignore such emails,
as is done in a third of 357 cases (\cite{teunis2015corresponding}):
it can be argued that no energy should be wasted on published code
and work on something new instead.
However, see \cite{barnes2010publish} for a better way to deal with this problem.
